---
title: "Web Scraping"
author: "Bastola"
date: "`r format(Sys.Date(), ' %B %d %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      collapse = TRUE, 
                      comment=NA, 
                      warning = FALSE,
                      message = FALSE,
                      fig.height = 4, fig.width = 6, fig.align='center')

library(tidyverse) 
library(lubridate)
library(stringr)
library(rvest)
```



## Your Turn 1

Here's the scraping code we just discussed:

```{r}
tables <- read_html("http://www.imdb.com/chart/top") %>%
  html_nodes("table") 

top250 <- html_table(tables[[1]])
```


- Why isn't `top250` data frame we just scraped tidy?

- Use your data-wrangling toolkit to create a tidy data set with columns: `rank`, `title`, `year`, and `imdb.rating`

*Answer:* The scraped data isn't tidy because

- The `Rank & Title` column contains three variables, and extra formatting `\n`.

```{r}
glimpse(top250)
```

Tidying the data:

```{r}
tidy_top250 <- 
  top250[,2:3] %>%  # Grab the middle two columns, select won't work with duplicate names
# fill in
# fill in

tidy_top250
```

You could also have used regular expressions instead of `parse_number()`

```{r}
tidy_top250 <- 
  top250[,2:3] %>%  # Grab the middle two columns, select won't work with duplicate names
 # fill in
 # fill in

tidy_top250 # notice that rank and year are still character vectors here

```

---------------------------------------------------

## Your turn 2


```{r}
url <- 'https://www.imdb.com/search/title/?groups=best_picture_winner&sort=year,desc&count=100&view=advanced'
webpage <- read_html(url)

```

- Use the selector gadget tool to find the CSS for extracting year the movie came out. 

- Tidy the data

  + Using `parse_number()`
  
  + Using regex


```{r}
# fill in
# fill in
```


---------------------------------------------------

## Your turn 3

```{r, echo=FALSE}
description_data_html <- html_nodes(webpage,'________________') %>% html_text() %>% ________()
head(description_data_html,3)
```

---------------------------------------------------

## Your turn 4

- Scrape the names, scores, and years of most popular TV shows on IMDB:
[www.imdb.com/chart/tvmeter](http://www.imdb.com/chart/tvmeter)

- Create a data frame called `tvshows` with four variables 
(`rank`, `name`, `score`, `year`)  

Note: 

It's easier to use the SelectorGadget and choose the CSS selectors wisely. Otherwise, you'll have more cleaning to do after scraping.


```{r}
page <- read_html("http://www.imdb.com/chart/tvmeter")
name <- page %>%
 # fill in
# fill in

ranks <- page %>%
  # fill in
 # fill in

scores <-  page %>%
  # fill in
# fill in

# If you don't use the gadget selector carefully, 
# there is more string manipulation needed here
years <- page %>%
 # fill in
# fill in

```


```{r}

tvshows <- tibble(
  rank = ranks,
  name = name,
  score = scores,
  year = years
)

tvshows
```


